Obtain metadata from Crossref Dump

### 2020-06-13 analysis/002_cr_els_matching.Rmd
match apc pricing list and elsevier data

---
title: "Obtain metadata from Crossref Dump"
output: html_notebook
---

@@

Possible reason:

@@

>>>>

---
title: "Obtain metadata from Crossref Dump"
output: github_document
---

@@

Possible reasons:

@@

### Create Crossref Elsevier subset in BQ

Upload list of Elsevier hybrid journals to BQ.

```{r}
els_jns_df <- readr::read_csv(here::here("data", "elsevier_apc_list.csv"))
els_jn_hybrid <- els_jns_df %>% 
  filter(oa_type == "Hybrid")
bq_els <- bq_table_create(
  "api-project-764811344545.cr_dump_march_20.elshybrid",
  fields =  els_jn_hybrid,
  friendly_name = "Elsevier hybrid journals May 2020",
  description = "The data was extracted from Elsevier APC pricing list, 
    downloaded 30 May 2020"
)
bq_table_upload(bq_els, els_jn_hybrid)
```

Create table with Crossref metadata for these journals since 2008.

```{sql, connection=con}
CREATE OR REPLACE TABLE `api-project-764811344545.cr_dump_march_20.els_hybrid_cr` AS
SELECT * FROM `api-project-764811344545.cr_dump_march_20.cr_08_20_expanded` as cr
WHERE EXISTS ( 
  SELECT 1 FROM `api-project-764811344545.cr_dump_march_20.elshybrid` as els_hybrid 
  WHERE (cr.issn = els_hybrid.issn)
  )
```

Descriptive:

By members

```{sql, connection=con}
SELECT  member, publisher, COUNT(DISTINCT(doi)) as articles
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`
WHERE issued_year > 2014 and issued_year < 2020
GROUP BY member, publisher
ORDER BY articles DESC
```

License prevalence

```{sql, connection=con}
SELECT REGEXP_REPLACE(license.URL, "http://|https://", "") as license_url, COUNT(DISTINCT(doi)) as articles
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`, unnest(license) as license
WHERE issued_year > 2014 and issued_year < 2020 AND license.content_version = 'vor'
GROUP BY license_url
ORDER BY articles DESC
```

License prevalence by days with delay

```{sql, connection=con, output.var="els_license_delay"}
SELECT 
  REGEXP_REPLACE(license.URL, "http://|https://", "") as license_url,
  license.delay_in_days,
  COUNT(DISTINCT(doi)) as articles
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`, unnest(license) as license
WHERE issued_year > 2014 and issued_year < 2020 AND license.content_version = 'vor'
GROUP BY license_url, license.delay_in_days
ORDER BY articles DESC
```

Immediate Licenses

```{r}
els_license_delay %>%
  filter(delay_in_days == 0)
```
